Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-15 hscc2017/paper.tex
wording

Recall that since the controller is synthesized in the $\mathbb{R}\param {I}{F}$
domain, $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$. 
However, given a real plant $\hat{G}(z)$, 
we need to introduce $\tilde G(z)=\mathcal{F}_{M_G,N_G}\param {I_p}{F_p}(\hat{G}(z))$, where 
%
\begin{align}
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
\vec{\tilde G} &=\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
\end{align}
%
where $\Delta_bc_i=\tilde{c}_i-\hat{c}_i$, 
and $\Delta_b{G}$ represents the plant uncertainty caused by
the rounding off effect.  We encompass the global uncertainty as
$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$.

%------------------------------------
\subsection{Closed-Loop Stability Verification under Parametric Uncertainties FWL Representation, and Quantisation Noise}
\label{sec:stability}
%------------------------------------

\aabatecmt{[Dario: please go through this section again, and clarify what sources of imprecision we consider where, distinguishing between plant and controller. also comment on why we operate on hat G rather than on tilde G - as we discussed yesterday. ]}
\dariocmt{I added a paragraph at the end of the section that should clarify.}
Sound synthesis of the digital controller requires the consideration of the effect of FWL on the controller, 
and of quantization disturbances in the closed-loop system.  
Let the quantizer $Q1$ (ADC) be the source of a white noise $\nu_{1}$, 
and $Q2$ (DAC) be the source of a white noise $\nu_{2}$.  The following equation
models the system in Figure~\ref{fig:sampledsystem}, encompassing the
parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
the controller $\tilde{C}(z)$:
%
\begin{equation}
\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\tilde{C}(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\tilde{C}(z)\hat{Y}(z). 
\end{equation}
%
The above can be rewritten as follows:
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\nu_{2}(z)+H_{3}(z) R(z),
\end{equation}
%
where
%
\begin{equation*}
H_{1}(z)=\frac{1}{1+\hat{G}(z) \tilde{C}(z)}, 
\end{equation*}
%
\begin{equation*}
H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)}, 
\end{equation*}
%
\begin{equation*}
H_{3}(z)=\frac{\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}. 
\end{equation*}

@@

A discrete-time dynamical system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if bounded inputs necessarily result in bounded outputs. 
This condition holds true over an LTI model if and only if every pole of its transfer function lies inside the unit circle \cite{Astrom08}.  
Analyzing Eq.~\eqref{eq:outputfunctions}, 
the following proposition provides conditions for the BIBO stability of the system in Figure~\ref{fig:sampledsystem}, 
with regards to the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded 
(in particular, the bound on the quantization noise is given by
Assumption~\ref{whitenoise}). 
%
\begin{myprop}{\cite{Bessa16,fadali}}
\label{prop:eq_int_stab} 
%
Consider a feedback closed-loop control system as given in
Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
controller $\tilde{C}(z) =\mathcal{F}_{M_C,N_C}\param {I}{F}(C(z))$ and uncertain discrete
model of the plant from~\eqref{eq:coefficients},\eqref{eq:delta_coefficients} 
%
$$
\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}, \quad \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}.
$$
%
Then $\hat{G}(z)$ is BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
\hspace{-3ex} S(z)=\tilde{C}_n(z)\hat{G}_n(z)+\tilde{C}_d(z)\hat{G}_d(z);
\end{equation}
\item the direct loop product $\tilde{C}(z) \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{myprop}

@@

If the verification is performed using FWL arithmetic, 
we note that the above equations must use $\tilde{G}(z)$ instead of $\hat{G}(z)$. 
The former will provide sufficient conditions for the latter to be stabilized.

>>>>

Recall that since the controller is synthesized in the $\mathbb{R}\param {I}{F}$
domain, $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$. 
However, given a real plant $\hat{G}(z)$, 
we need to introduce $\tilde G(z)=\mathcal{F}_{M_G,N_G}\param {I_p}{F_p}(\hat{G}(z))$, where 
%
\begin{align}
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
\vec{\tilde G} &=\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
\end{align}
%
where $\Delta_bc_i=\tilde{c}_i-\hat{c}_i$, and $\Delta_b{G}$ represents the
plant uncertainty caused by the rounding off effect.  We capture the global
uncertainty as $\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$.

%------------------------------------
\subsection{Closed-Loop Stability Verification under Parametric
Uncertainties, FWL Representation and Quantisation Noise}
\label{sec:stability}
%------------------------------------

\aabatecmt{[Dario: please go through this section again, and clarify what sources of imprecision we consider where, distinguishing between plant and controller. also comment on why we operate on hat G rather than on tilde G - as we discussed yesterday. ]}
\dariocmt{I added a paragraph at the end of the section that should clarify.}
%
Sound synthesis of the digital controller requires the consideration of the
effect of FWL on the controller, and of quantization disturbances in the
closed-loop system.  Let the quantizer $Q1$ (ADC) be the source of a white
noise $\nu_{1}$, and $Q2$ (DAC) be the source of a white noise~$\nu_{2}$. 
The following equation models the system in Figure~\ref{fig:sampledsystem},
including the parametric uncertainties $\Delta \vec{G}$ and the FWL
effects on the controller $\tilde{C}(z)$:
%
\begin{equation}
\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\tilde{C}(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\tilde{C}(z)\hat{Y}(z). 
\end{equation}
%
The above can be rewritten as follows:
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\nu_{2}(z)+H_{3}(z) R(z),
\end{equation}
%
where
%
\begin{equation*}
H_{1}(z)=\frac{1}{1+\hat{G}(z) \tilde{C}(z)}, 
\end{equation*}
%
\begin{equation*}
H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)}, 
\end{equation*}
%
\begin{equation*}
H_{3}(z)=\frac{\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}. 
\end{equation*}

@@

A discrete-time dynamical system is said to be Bounded-Input and
Bounded-Output (BIBO) stable if bounded inputs necessarily result in bounded
outputs.  This condition holds true over an LTI model if and only if every
pole of its transfer function lies inside the unit circle \cite{Astrom08}. 
Analyzing Eq.~\eqref{eq:outputfunctions}, the following proposition provides
conditions for the BIBO stability of the system in
Figure~\ref{fig:sampledsystem}, with regards to the exogenous signals
$R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded (in particular, the
bound on the quantization noise is given by Assumption~\ref{whitenoise}).
%
\begin{myprop}{\cite{Bessa16,fadali}}
\label{prop:eq_int_stab} 
%
Consider a feedback closed-loop control system as given in
Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
controller $\tilde{C}(z) =\mathcal{F}_{M_C,N_C}\param {I}{F}(C(z))$ and
uncertain discrete model of the plant
from~\eqref{eq:coefficients}, \eqref{eq:delta_coefficients}
%
$$
\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}, \quad \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}.
$$
%
Then $\hat{G}(z)$ is BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
\hspace{-3ex} S(z)=\tilde{C}_n(z)\hat{G}_n(z)+\tilde{C}_d(z)\hat{G}_d(z);
\end{equation}
\item the direct loop product $\tilde{C}(z) \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{myprop}

@@

If the verification is performed using FWL arithmetic,  the above equations
must use $\tilde{G}(z)$ instead of $\hat{G}(z)$.  The former will provide
sufficient conditions for the latter to be stabilized.
